Appendix I

### 2018-04-20 AppendixI.Rmd
results

**Figure A2**: Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3 \@ref(fig:FigSeedMassClasses).

**Figure A3**: Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes. \@ref(fig:DivFunAppendix).

@@

# Figure A1

@@

# Figure A2

@@

# Figure A3

>>>>

**Figure A2**: Trajectories of the distance to initial condition of the 30 sampled years in the two-dimensional space from the NMDS of v taxonomic composition at genus level and (ref:Boldb) functional composition. Distance are abundance-based Bary-Curtis metric. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3). The 0.025 and 0.975 percentile correspond to the variance observed for 50 iteration of the taxonomic uncertainty propagation and functional trait filling processes.

**Figure A3**: Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3 \@ref(fig:FigSeedMassClasses).

**Figure A4**: Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes. \@ref(fig:DivFunAppendix).

@@

# **Figure A1**: Bayesian process sheme

@@

# **Figure A2**: Dissimilarity to initial inventory of plots taxonomic and functional composition

```{r NMDSdivergence, out.width = '80%', fig.asp = 1.2/2, echo=FALSE,fig.cap="Trajectories of the distance to initial condition of the 30 sampled years in the two-dimensional space from the NMDS of v taxonomic composition at genus level and (ref:Boldb) functional composition. Distance are abundance-based Bary-Curtis metric. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3). The 0.025 and 0.975 percentile correspond to the variance observed for 50 iteration of the taxonomic uncertainty propagation and functional trait filling processes.", fig.env="figure*"}
load("DB/FunctionalComposition_forGraph")
load("DB/TaxoComposition_forGraphs")

TaxoDist(MatrepTaxo)
FunDist(MatrepFun)

# **Figure A3**: Proportion of seed mass classes along time

@@

# **Figure A4**: Rao diversity trajectories with all plots display

### 2018-04-20 AppendixI.tex
results

\textbf{Figure A2}: Trajectories of seed mass classes proportions over
30 years after disturbance, corresponding to the median (solid line) and
0.025 and 0.975 percentile (gray envelope) observed after 50 iteration
of the taxonomic uncertainty propagation. No gap filling process was
applied in this case. Initial treatments are represented by solid lines
colors with green for control, blue for T1,orange for T2 and red for T3
\ref{fig:FigSeedMassClasses}.

\textbf{Figure A3}: Trajectories of the Rao functional diversity over 30
years after disturbance. Trajectories correspond to the median (solid
line) and 0.025 and 0.975 percentile (gray envelope) observed after 50
iteration of the taxonomic uncertainty propagation. Initial treatments
are represented by solid lines colorswith green for control, blue for
T1,orange for T2 and red for T3.and the missing trait value filling
processes. \ref{fig:DivFunAppendix}.

@@

\section{Figure A1}\label{figure-a1}

@@

\section{Figure A2}\label{figure-a2}

@@

\section{Figure A3}\label{figure-a3}

>>>>

\textbf{Figure A2}: Trajectories of the distance to initial condition of
the 30 sampled years in the two-dimensional space from the NMDS of v
taxonomic composition at genus level and (ref:Boldb) functional
composition. Distance are abundance-based Bary-Curtis metric. Line
colors represent the disturbance treatment (green for control, blue for
T1,orange for T2 and red for T3). The 0.025 and 0.975 percentile
correspond to the variance observed for 50 iteration of the taxonomic
uncertainty propagation and functional trait filling processes.

\textbf{Figure A3}: Trajectories of seed mass classes proportions over
30 years after disturbance, corresponding to the median (solid line) and
0.025 and 0.975 percentile (gray envelope) observed after 50 iteration
of the taxonomic uncertainty propagation. No gap filling process was
applied in this case. Initial treatments are represented by solid lines
colors with green for control, blue for T1,orange for T2 and red for T3
\ref{fig:FigSeedMassClasses}.

\textbf{Figure A4}: Trajectories of the Rao functional diversity over 30
years after disturbance. Trajectories correspond to the median (solid
line) and 0.025 and 0.975 percentile (gray envelope) observed after 50
iteration of the taxonomic uncertainty propagation. Initial treatments
are represented by solid lines colorswith green for control, blue for
T1,orange for T2 and red for T3.and the missing trait value filling
processes. \ref{fig:DivFunAppendix}.

@@

\section{\texorpdfstring{\textbf{Figure A1}: Bayesian process
sheme}{Figure A1: Bayesian process sheme}}\label{figure-a1-bayesian-process-sheme}

@@

\section{\texorpdfstring{\textbf{Figure A2}: Dissimilarity to initial
inventory of plots taxonomic and functional
composition}{Figure A2: Dissimilarity to initial inventory of plots taxonomic and functional composition}}\label{figure-a2-dissimilarity-to-initial-inventory-of-plots-taxonomic-and-functional-composition}

{\centering \includegraphics[width=0.8\linewidth]{AppendixI_files/figure-latex/NMDSdivergence-1}

\caption{Trajectories of the distance to initial condition of the 30 sampled years in the two-dimensional space from the NMDS of v taxonomic composition at genus level and (ref:Boldb) functional composition. Distance are abundance-based Bary-Curtis metric. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3). The 0.025 and 0.975 percentile correspond to the variance observed for 50 iteration of the taxonomic uncertainty propagation and functional trait filling processes.}\label{fig:NMDSdivergence}
\end{figure*}

\section{\texorpdfstring{\textbf{Figure A3}: Proportion of seed mass
classes along
time}{Figure A3: Proportion of seed mass classes along time}}\label{figure-a3-proportion-of-seed-mass-classes-along-time}

@@

\section{\texorpdfstring{\textbf{Figure A4}: Rao diversity trajectories
with all plots
display}{Figure A4: Rao diversity trajectories with all plots display}}\label{figure-a4-rao-diversity-trajectories-with-all-plots-display}

### 2018-04-20 WholePlotTrajectories.tex
results

To counter the remaining taxonomic uncertainty plots taxonomic
composition and diversity were analysed at the genus level, \emph{i.e.}
referring to the genus of observed or trialed botanical names. The
analysis of taxonomic and functional composition of plots along time was
visualized in a two-dimensional ordination space based on non-metric
dimensional scaling of succesive floristic or functional inventories.
Plots trajectories along time was reported comparatively to the
inventories in 1989, 5 years after disturbance, which corresponded to
first inventory with a sufficient degree of uncertainty (\textless{}30\%
of undetermined trees). The inventories dissimilarity compared to the
reference 1989 inventory was reported using occurrence-based (Jaccard)
and abundance-based (Bray-Curtis) similarity measures. The trajectory of
inventories along time was visualized with the euclidean distance in the
two-dimensional ordination space to the 1989 inventory. The functional
trajectories of the leaf and stem and life traits were also visualized
with the community weighted means (CWM), representing the average trait
value in a community weighted by relative abundance of the species
carrying each value \citep{Diaz2007, Garnier2004}. Species seed mass
corresponded to 5 classes of increasing mass, seed mass trajectories
were therefore reported as the proportion of each class in the
inventories.

@@

Over time, 828388 trees and 591 botanical species pertaining to 223
genus and 64 botanical families were recorded. Trajectories of taxonomic
and functional composition after disturbance were examined through the
ordination of successive inventories from 1989 (5 years after
disturbance) in the two-dimensional space from NMDS analysis based on
flora inventories and the corresponding functional composition.
Classifications were performed using either abundance-based Bray-Curtis
(Figure \ref{fig:NMDSplans}) or incidence-based Jaccard dissimilarity
(data not shown).

Both taxonomic and functional composition were substantially affected by
disturbance, and the maximum dissimilarity to 1984 reference inventory
composition was positively correlated with the disturbance intensity.
Until 30 years after disturbance, all disturbed plots taxonomic
composition remained significantly dissimilar to that of the 1989
reference inventory composition (Figure \ref{fig:NMDSplans}). All plots,
though, displayed a unimodal trajectory with a the return toward the
taxonomic and functional composition of the 1989 reference inventory
suggesting a shift towards a cyclic regime (Figure
\ref{fig:NMDSdivergence}). For taxonomic composition, the maximum
dissimilarity to 1984 inventory composition was reach around 20 years
after disturbance for the T2 and T3 plots and for one T1 plot while
control and other T1 plots continued to increase (Figure
\ref{fig:NMDSdivergence}.a). For functional composition, the maximum
dissimilarity to 1984 inventory composition was reach from 15 to 20
years after disturbance for the T2 and T3 plots while T1 and control
plots continued to increase (Figure \ref{fig:NMDSdivergence}.b). The
functional composition distancing from the reference inventory was also
positively correlated with disturbance intensity and similarly
stabilized or reduced (for 5 of T1, T2 and T3 plots) from 20 years after
disturbance (Figure \ref{fig:NMDSdivergence}).

The coordinates of the functional traits were measured in the
two-dimensional ordination space that mapped plots evolution along time
(graphs not showed) revealed a trajectory of disturbed plots toward
acquisitive functional strategies (from high WD to high SLA and
chlorophyll content).

@@

{\centering \includegraphics[width=0.8\linewidth]{WholePlotTrajectories_files/figure-latex/NMDSdivergence-1}

\caption{Trajectories of the distance to initial condition of the 30 sampled years in the two-dimensional space from the NMDS of v taxonomic composition at genus level and \textbf{(b)} functional composition. Distance are abundance-based Bary-Curtis metric. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3). The 0.025 and 0.975 percentile correspond to the variance observed for 50 iteration of the taxonomic uncertainty propagation and functional trait filling processes.}\label{fig:NMDSdivergence}
\end{figure*}

@@

For all plots the trajectories of the community weighted means (CWM)
were drawn for the 8 functional and life history traits (Leaf thickness,
chlorophyll content, toughness and specific area,wood specific gravity
and barck thickness and seed mass and maximum adult height) (Figure
\ref{fig:CWM}).

To compensate the intrinsinc difference among plots the trajectories
drawn correspond to the difference in value between the reference
inventory in 1984 (5 year after disturbance) and the successive years
inventoried.

@@

For undisturbed plots the Richness, Shannon and Simpson diversity
remained comparable to the initial values 5 years after disturbance.
After disturbance, the richness increased after low disturbance
intensity, with a maximum increase of 14 botanical genuses (for plot 3
after treatment 2), but followed a unimodal decrease with a return to
initial values after intense disturbance. The taxonomic evenness
(Shannon and Simpson diversities), however, significantly increased
after all disturbance regime. The evenness followed a unimodal
trajectory with a just beginning return towards initial values and a
maximum reached around 20 years and positively correlated to the
disturbance intensity (\(\rho_{spearman}^{Shannon}=0.92\), and
\(\rho_{spearman}^{Simpson}=0.97\)). Only two T3 plots, plots 8 and 12,
remained increasing 30 years after disturbance \ref{fig:DivTaxo}),
suggesting a similar be much delayed unimodal trajectory.

>>>>

To counter the remaining taxonomic uncertainty plots taxonomic
composition and diversity were analysed at the genus level, \emph{i.e.}
referring to the genus of observed or trialed botanical names.
Variations in plots taxonomic and functional composition after
disturbance was visualized by their trajectories in a two-dimensional
ordination space over 30 years. Two NMDS were conducted, either from
taxonomic flora inventories or from plots functional composition based
on the 8 leaf, stem and life history traits. Plots trajectories along
time was reported comparatively to the inventories in 1989, 5 years
after disturbance, which corresponded to first inventory with a
sufficient degree of uncertainty (\textless{}30\% of undetermined
trees). The inventories dissimilarity compared to the reference 1989
inventory was reported using occurrence-based (Jaccard) and
abundance-based (Bray-Curtis) similarity measures. The trajectory of
inventories along time was visualized with the euclidean distance in the
two-dimensional ordination space to the 1989 inventory. The trajectories
of the leaf and stem and life traits were also visualized with the
community weighted means (CWM), representing the average trait value in
a community weighted by relative abundance of the species carrying each
value \citep{Diaz2007, Garnier2004}. To compensate the intrinsinc
difference among plots the trajectories corresponded to the differences
along time with the reference inventory in 1984 (5 year after
disturbance). Species seed mass corresponded to 5 classes of increasing
mass, seed mass trajectories were therefore reported as the proportion
of each class in the inventories.

@@

Over time, 828388 trees and 591 botanical species pertaining to 223
genus and 64 botanical families were recorded. Taxonomic and functional
plots trajectories were examined through the ordination in a two
dimensional ordiantion space of successive inventories from 1989 (5
years after disturbance) to 2015 (31 years after disturbance).
Classifications were performed using either abundance-based Bray-Curtis
(Figure \ref{fig:NMDSplans}) or incidence-based Jaccard dissimilarity,
this last having given similar results (data not shown).

Both taxonomic and functional composition of disturbed plots followed
consistent trajectories over time, translating compositional changes
while control plots remained stable. The addition of functional traits
in the two dimensional space revealed a shift of plots composition
towards more acquisitive functional strategies (disturbed plots changed
from high average WD to high average SLA and chlorophyll content). The
dissimilarity of the successive inventories for disturbed plots compared
to their respective reference inventory in 1989 followed unimodal
trajectories (AppendixI, Figure A2). The maximum dissimilarity of plot
strajectories was positively correlated to the disturbance intensity for
taxonomic (\(\rho_{spearman}^{taxonomic}=0.91\)) as well as functional
composition (\(\rho_{spearman}^{taxonomic}=0.96\)). The time at maximum
dissimilarity for taxonomic composition was reached around 26 years
after disturbance while it was 22 years for functional composition. All
trajectories returned towards the initial composition and translated
cyclic compositional changes as visualized in figure (Figure
\ref{fig:NMDSplans}).

@@

@@

The changes observed in plots functional composition went hand to hand
with consistent trajectories of the 8 functional and life history traits
(Leaf thickness, chlorophyll content, toughness and specific area,wood
specific gravity and barck thickness and seed mass and maximum adult
height) visaualized with plots community weighted means (CWM) (Figure
\ref{fig:CWM}).

@@

For undisturbed plots the Richness, Shannon and Simpson diversity
remained comparable to the initial values 5 years after disturbance.
After disturbance, the richness increased after low disturbance
intensity, with a maximum increase of 14 botanical genuses (for plot 3
after treatment 2), but followed a unimodal decrease with a return to
initial values after intense disturbance. The taxonomic evenness
(Shannon and Simpson diversities), however, significantly increased
after all disturbance regime. The evenness followed a unimodal
trajectory with a just beginning return towards initial values and a
maximum reached around 20 years and positively correlated to the
disturbance intensity (\(\rho_{spearman}^{Shannon}=0.86\), and
\(\rho_{spearman}^{Simpson}=0.89\)). Only two T3 plots, plots 8 and 12,
remained increasing 30 years after disturbance \ref{fig:DivTaxo}),
suggesting a similar be much delayed unimodal trajectory.
